\documentclass[margin,line]{res}

%This lets me make hyper references to BYU and Georgia Tech
\usepackage{etoolbox}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{etaremune}
\PassOptionsToPackage{hyphens}{url}
\usepackage[colorlinks=false]{hyperref}
\usepackage[table, dvipsnames]{xcolor}

% define fonts
%\usepackage{fontspec}
%\setmainfont[Mapping=tex-text]{Palatino}
%\newfontface\acc{Marcellus SC}

\usepackage{needspace}
\newcommand{\acc}{\scshape }
\def\r{\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}}
\let\oldsection\section\renewcommand{\section}[1]{\r \oldsection{\scshape{#1}}}

% Define a macro to color a row of a table. https://tex.stackexchange.com/a/413008/12874
\makeatletter
\g@addto@macro{\endtabular}{\rowfont{}}% Clear row font
\makeatother
\newcommand{\rowfonttype}{}% Current row font
\newcommand{\rowfont}[1]{% Set current row font
\gdef\rowfonttype{#1}#1\ignorespaces%
}
\makeatother

% page numbers
\usepackage{fancyhdr}
\pagestyle{fancy}
\setlength{\headheight}{12.0pt} % Add this line to fix the warning
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\oddsidemargin-.5in
\evensidemargin-.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

% if detailtrue, then the CV will show notes on publication venue
% as well as student evaluations for each course.
\newif\ifdetail{}
\ifcsdef{myvar}{\myvar}{}

%\detailtrue

%% ==========================================
%This allows me to use Bibtex to create my publication list
%\usepackage{natbib}
%\makeatletter
%\renewenvironment{thebibliography}[1]
%     {%\section*{\bibname}% <-- remove this to make section naming correct
%      \@mkboth{\MakeUppercase\bibname}{\MakeUppercase\bibname}%
%      \list{\@biblabel{\@arabic\c@enumiv}}%
%           {\settowidth\labelwidth{\@biblabel{#1}}%
%            \leftmargin\labelwidth
%            \advance\leftmargin\labelsep
%            \@openbib@code
%            \usecounter{enumiv}%
%            \let\p@enumiv\@empty
%            \renewcommand\theenumiv{\@arabic\c@enumiv}}%
%      \sloppy
%      \clubpenalty4000
%      \@clubpenalty \clubpenalty
%      \widowpenalty4000%
%      \sfcode`\.\@m}
%     {\def\@noitemerr
%       {\@latex@warning{Empty `thebibliography' environment}}%
%      \endlist}
%\makeatother

%\usepackage[resetlabels]{multibib}
%  \newcites{j,c,w}{{Test},{Test1},{Test2}}
% j- journals c-conferences p-presentations
\setdescription{font=\normalfont}

%% ==========================================
% This defines the list types and formatting
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\newcounter{enuminitialize}

\newenvironment{myenum}[1][]
{%
 \setcounter{enuminitialize}{#1}
 \addtocounter{enuminitialize}{2}
 \begin{enumerate}[left= 4pt, itemsep=8pt, start=\value{enuminitialize}, label=\arabic*\addtocounter{enumi}{-2}]
}
{%
 \end{enumerate}
}




\begin{document}
% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\LARGE\scshape Gregory S.  Macfarlane}
\vspace{.05in}
 \moveleft.5\hoffset\centerline{Brigham Young University}
 \moveleft.5\hoffset\centerline{
	 \href{mailto:gregmacfarlane@byu.edu}{gregmacfarlane@byu.edu}
   801.422.8505}
\vspace{.05in}
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{430 Engineering Building}
 \moveleft.5\hoffset\centerline{Provo, UT 84602}

\begin{resume}

%\section{\sc Contact\\ Information}
\vspace{.05in}



%% ============================================================================


%\textit{ Research Interests ---} Passive data and its applications in transport and
%land use modeling and forecasting.
%% ============================================================================
\oldsection{\scshape Post-Graduate\\ Employment}

{\acc{Brigham Young University}}

\begin{list1}
\item[] \textit{Assistant Professor} \hfill {November 2018 ---}
\end{list1}

{\acc{University of North Carolina, Chapel Hill}}

\begin{list1}
\item[]\textit{Adjunct Lecturer/Teaching Assistant} \hfill {January 2017 --- May 2017}
\end{list1}

{\acc{Transport Foundry}} 
\begin{list1}
  \item[] \textit{Transportation Engineer} \hfill {April 2017 --- October 2018}
\end{list1}

{\acc{WSP | Parsons Brinckerhoff}} 

\begin{list1}
  \item[] \textit{Technical Principal, Systems Analysis Group} \hfill {October 2016 --- April 2017}
  \item[] \textit{Transportation Engineer} \hfill{June 2014 --- September 2016}
\end{list1}

{\acc{Georgia Institute of Technology}}

\begin{list1}
\item[]\textit{Post-doctoral Researcher} \hfill {January 2014 --- May 2014}\\
\end{list1}


\vspace{-.4cm}
\section{Research\\ Interests}
Transportation planning and engineering, travel demand modeling,
passive transportation data, spatial and social correlation.

Registered professional engineer in North Carolina, license \#044518

\section{Education}
\href{http://www.gatech.edu}{\acc Georgia Institute of Technology}
\\
	\vspace*{-.1in}
	\begin{list1}
	\item[] Ph.D., Transportation Systems Engineering \hfill{May 2014} 

%	\begin{list2}
%  	\item[] Advisor: Laurie A. Garrow
%		\item[] Dissertation: ``Using Big Data to Model Travel Behavior: Applications to Vehicle Ownership and Willingness-to-Pay for Transit Accessibility''
%%		\item[] GPA: 3.86/4.0
%%		\item[] Committee: Laurie A. Garrow (Chair - CEE), Juan Moreno-Cruz
%%(Economics), \\ Patricia L. Mokhtarian (CEE), Kari E. Watkins (CEE), Patrick S.
%%McCarthy (Economics), Jeffrey P. Newman (CEE)
%  \end{list2}
	\vspace*{.05in}
	\item[]M.S., Economics \hfill{May 2014}
	\end{list1}

\href{http://www.byu.edu}{\acc Brigham Young University}
\\
\vspace*{-.1in}
\begin{list1} 
  \item[] B.S. with University Honors, Civil Engineering \hfill{December 2009}
  \item[] Minor degrees in Mathematics and Asian Studies
%  \begin{list2}
%		\item[] Honors Thesis: ``Delay Patterns
%			and Perceptions at Free Right-turn Channelized Intersections''
%		\item[] Advisor: Mitsuru Saito
%%		\item[] GPA: 3.7/4.0
%    \item[] Studies Abroad: Nanjing, China (Engineering);
%			Naples, Italy (Arch{\ae}ology)
%	\end{list2}
\end{list1}
%% ============================================================================
%\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}

%% ==========================================
% BibTex reference management

% Journal Articles
%\section{\secfont Under \\ Review}
%\bibentry{epb_parkaccess}


\ifdetail 
\section{Papers in Production}
These are manuscripts that have not been published, but are either under review or being prepared for submission.
The marking $^\dagger$indicates BYU graduate student authors, $^*$indicates BYU undergraduate authors.
{\color{NavyBlue} Throughout this document, work completed since my third year review appears in blue.}

\vspace{.3cm}
\begin{myenum}[7]
  {\color{NavyBlue} 
  \item Erhardt, G.D., Guan, H.Z. Lee, D., \textbf{Macfarlane, G.S.}, Van Hentenryck,
  P. Comprehensive studies on on-demand multimodal transit systems with
  two case studies in San Francisco and Salt Lake City. Working paper. Anticipated submission in Winter 2026.

  \item Tenenboim, E., Xu, Y., Erhardt, G.D.,  \textbf{Macfarlane, G.S.}, \&
  Peeta, S.  A model of ride-hailing driver participation: shift duration, start
  time, and start location. Working paper. Anticipated submission in Winter 2026.

  \item Day, C.$^\dagger$, \textbf{Macfarlane, G.S.}, Atchley, S.H.$^*$, Erhardt, G.D., Ven Hentenryck, P., Watkins, K.E. 
  Implementation and quantitative evaluation of multi-modal optimization and simulation for transit and ridehail competitive analysis. 
  Working paper. Anticipated submission in Winter 2026.

  \item Lu, R., Ji, J.Y., Wang, L.M., Belkessa, L., Dong, Y., Madadi, B.,
  Varotto, S., Saunier, N., \textbf{Macfarlane, G.S.}, Ghosh, B., Ameli, M., \&
  Wu, C. Towards accelerating transportation research: measuring the practice of
  open science. Working paper. Anticipated submission in Fall 2025.

  \item Sivakumar, A., Jones, P. M\"ockel, R., Moreno Chou, A.T., Erhardt, G.,
  \textbf{Macfarlane, G.S.}. The ‘activity-based’ approach: a new
  perspective for addressing the major environmental and resource challenges
  faced by societies. Working paper. Anticipated submission in Summer 2025.

  \item Youngs, E.K.$^\dagger$, \textbf{Macfarlane, G.S.}, Nielsen, J.A.
  Exploring the link between travel behavior and mental health. Working paper.
  Anticipated submission in Summer 2025.

  \item \textbf{Macfarlane, G.S.}, Stucki, E.$^\dagger$, Redelfs, A.H.,
  Spruance, L.A. (2025). Where’s dinner coming from? A utility-based
  investigation of access to nutrition in Utah. Received second revise and
  resubmit at \textit{Journal of Transport and Land Use}.

}

\end{myenum}
 \fi

\section{Refereed \\ Journal\\ Articles}
These are manuscripts that have been published, or accepted for publication.
The marking $^\dagger$indicates BYU graduate student authors, and $^*$indicates
BYU undergraduate authors. 

\ifdetail 
First author or first faculty author on 12 of 21  total journal articles, indicating primary responsibility for the work.
Paper 1 came from my undergraduate work, papers 2 through 6 were from my doctoral research, and
papers 7 onward represent work completed during my time on the faculty at BYU. Number of citations
are from Google Scholar as of August 2025.  
For recent papers, I provide a short description of my role in the work.
Notes on the venues where I publish including impact factors and rankings are provided 
in the section following. 
\fi
\vspace{.3cm}

\begin{myenum}[21]

  \ifdetail{\color{NavyBlue} \fi

  \item Voulgaris, C.T., Fjendbo-Jensen, A.,  \textbf{Macfarlane, G.S.}
  (2025). You'll Never Walk Alone: Parental active escorting as an alternative
  to car travel to school. \textit{Journal of Transport \& Health}, 44, 102147. \url{https://doi.org/10.1016/j.jth.2025.102147}

  \ifdetail I provided econometric support for this paper, which is the beginning of an international collaborative effort looking at the travel 
  choices of children and families. \fi

  \item Gibbons, N.$^\dagger$  \& \textbf{Macfarlane, G.S.} (2025). 
  Evaluating the impacts of parameter uncertainty in a practical transportation
  demand model. \textit{Future Transportation}, 5 (1), 15. \url{https://doi.org/10.3390/futuretransp5010015}

  \ifdetail This paper is the result of Natalie Gibbon's MS thesis which I supervised, and came as an outgrowth of my UDOT-funded
  research on transportation network resilience. \fi

  \item \textbf{Macfarlane, G.S.}, Barnes, M.$^\dagger$, \& Gibbons, N.$^*$ (2025). 
  A utility-based approach to modeling systemic resilience of highway networks with an application in Utah.
  \textit{Journal of Transportation Engineering Part A: Systems}. 151 (1). \url{https://ascelibrary.org/doi/10.1061/JTEPBS.TEENG-8534}

  \ifdetail This paper is drawn from the results of Max Barnes' MS thesis which I supervised; this was the first UDOT-funded project which I secured as a new faculty member. \fi

  \item Wang, B.$^\dagger$, Fulda, N., Huang, Z.Y.$^*$, Schultz, G.G., \textbf{Macfarlane, G.S.}, Arnesen, J.$^*$, Khayyat, A.$^*$ (2024). 
  Predicting directional traffic volume at intersections with automated traffic signal performance measures data using machine learning algorithms.
 \textit{Transportation Research Record}. \url{https://doi.org/10.1177/03611981241252829}

  \ifdetail This paper was the result of a multidisciplinary collaboration with Grant Schultz's PhD student and multiple undergraduates in the Computer Science program. I helped the student researchers to frame the problem and evaluated the model output. \textbf{Citations: 2}\fi

  \item \textbf{Macfarlane, G.S.}, Riches, G.$^\dagger$, Youngs, E.K.$^\dagger$,
  Nielsen, J.A. (2024). Classifying location points as daily activities using
  simultaneously optimized DBSCAN-TE parameters.  \textit{Findings}.
  \url{https://doi.org/10.32866/001c.116197}
  
  \ifdetail This paper is the result of exploratory work that comprised Gillian Riches' MS thesis, where she adapted an algorithm to process data that was then used in Emily Youngs' MS thesis. This paper was well-suited to the open-access, concise format of \textit{Findings}. \fi 

  \item Voulgaris, C.T., \textbf{Macfarlane, G.S.}, Kaylor, J. (2024).
  Whose miles are these anyway? Estimating site-generated vehicle miles traveled.
  \textit{Journal of the American Planning Association}. 90(4), 593--609 \url{https://doi.org/10.1080/01944363.2023.2298962}

  \ifdetail This is the result of a collaboration with Carole Voulgaris at Harvard and Joseph Kaylor of ARUP (a consulting firm) where we used data from my lab's travel demand model runs to comment on California's attempts to replace traffic Level of Service in impact assessments. \textbf{Citations: 1}\fi

  \item  Wang, B.$^\dagger$, Schultz, G.G., \textbf{Macfarlane, G.S.}, Eggett, D.L., 
  \& Davis, M.C.$^*$ (2023) A methodology to detect traffic data anomalies in automated traffic 
  signal performance measures. \textit{Future Transportation}. 3(4), 1175-1194. \url{https://doi.org/10.3390/futuretransp3040064} 
  
  \ifdetail I was Co-PI on a UDOT-funded project that resulted in a portion of Bruce Wang's PhD and this related paper. I supported the data management and analysis tasks. \textbf{Citations: 3}\fi

  \item Daines, T.J.$^\dagger$, Schultz, G.G., \textbf{Macfarlane, G.S.}, \&
  Ward, C.$^*$ (2022). Evaluating real time ramp meter queue length estimation.
  \textit{Future Transportation}, 2(4), 807-827. \url{https://doi.org/10.3390/futuretransp2040045}

  \ifdetail I was Co-PI on a UDOT-funded project that resulted in Tanner Daines' MS thesis and this related paper. I supported the data management and analysis tasks. \textbf{Citations: 3}. \fi


  \item \textbf{Macfarlane, G.S.}, Stucki, E.$^\dagger$, Redelfs, A.H., \& Spruance, L.A. (2022).
  Beyond proximity: utility-based access from location-based services data.
  \textit{International Journal of Environmental Research and Public Health}, 19(19), 12352.
  \url{https://doi.org/10.3390/ijerph191912352}.

  \ifdetail This was preparatory work pursued by my MS Student Emma Stucki ahead of her MS thesis. \textbf{Citations: 1} \fi

  \item \textbf{Macfarlane, G.S.}, Voulgaris, C.T., \& Tapia, T. (2022).
  City parks and slow streets: a utility-based access and equity analysis.
  \textit{Journal of Transport and Land Use}. 15(1): 587-612.
  \url{https://doi.org/10.5198/jtlu.2022.2009}

  \ifdetail This paper develops a new method to examine accessibility using location-based services data, and is notable for providing a policy analysis of COVID-19 related street-to-park conversions. \textbf{Citations: 10} \fi

  \item Wang, B.$^\dagger$, Schultz, G.G., \textbf{Macfarlane, G.S.}, \& McCuen,
  S.$^*$ (2022). Evaluating signal systems using automated traffic signal
  performance measures. \textit{Future Transportation}. 2(3):  659-674.
  \url{https://doi.org/10.3390/futuretransp2030036}.

  \ifdetail This paper was the result of a UDOT-funded project and supported Bruce Wang's Ph.D. I supported the project's data analysis and modeling. \textbf{Citations: 9} \fi


  \ifdetail }\fi

  \item \textbf{Macfarlane, G.S.}, Sheffield, M.H.$^\dagger$, Bennet, L.S.$^\dagger$, \& Schultz, G.G. (2021).
  The effect of transit signal priority on bus rapid transit headway adherence.
  \textit{Findings}. \url{https://doi.org/10.32866/001c.24499}.
  \ifdetail \textbf{Citations: 2} \fi

  \item\textbf{Macfarlane, G.S.}, Hunter, C.$^*$, Martinez, A.$^*$, \& Smith, E.$^*$  (2021).
  Rider perceptions of an on-demand microtransit service in Salt Lake County, Utah
  \textit{ Smart Cities} 4(2): 717-727.  \url{https://doi.org/10.3390/smartcities4020036} 
  \ifdetail \textbf{Citations: 22}\fi

  \item\textbf{Macfarlane, G.S.}, Boyd, N., Taylor, J.E., \& Watkins, K. (2021) Modeling the impacts of park access
on health outcomes: A utility-based accessibility approach. \textit{ Environment and
Planning B: Urban Analytics and City Science}, 48(8), 2289–2306. \url{https://doi.org/10.1177/2399808320974027}
  \ifdetail \textbf{Citations: 31}\fi

  \item Glenn, J., Bluth, M.$^*$, Christianson, M.$^*$, Pressley, J.$^*$, Taylor, A., \textbf{Macfarlane, G.S.}, \& Chaney, R. A. (2020).
  Considering the potential health impacts of electric scooters: an analysis of user reported behaviors in Provo, Utah.
  \textit{ International Journal of Environmental Research and Public Health}, 17(17), 6344. \url{https://doi.org/10.3390/ijerph17176344} 
  \ifdetail \textbf{Citations: 79}\fi

  \item\textbf{Macfarlane, G.S.}, Garrow, L.A., \& Moreno-Cruz, J. (2015). Do Atlanta
residents value MARTA? Selecting an autoregressive model to recover willingness
to pay. \textit{ Transportation Research Part A: Policy and Practice}, 78, 214–230.
\url{https://doi.org/10.1016/j.tra.2015.05.010} \ifdetail \textbf{Citations: 10} \fi

  \item\textbf{Macfarlane, G.S.}, Garrow, L.A., \& Mokhtarian, P. L. (2015). The influences of
past and present residential locations on vehicle ownership decisions.
\textit{ Transportation Research Part A: Policy and Practice}, 74, 186–200.
\url{https://doi.org/10.1016/j.tra.2015.01.005} \ifdetail \textbf{Citations: 55} \fi

  \item Brakewood, C., \textbf{Macfarlane, G.S.}, \& Watkins, K.E. (2015). The impact of
real-time information on bus ridership in New York City. \textit{ Transportation Research
Part C: Emerging Technologies}, 53, 59–75. \url{https://doi.org/10.1016/j.trc.2015.01.021} 
\ifdetail \textbf{Citations: 231} \fi

  \item Binder, S., \textbf{Macfarlane, G.S.}, Garrow, L.A., \& Bierlaire, M. (2014).
Associations among household characteristics, vehicle characteristics and
emissions failures: An application of targeted marketing data. \textit{ Transportation
Research Part A: Policy and Practice}, 59, 122–133.
\url{https://doi.org/10.1016/j.tra.2013.11.005}\ifdetail\ \textbf{Citations: 19} \fi

  \item Wall, T.A., \textbf{Macfarlane, G.S.}, \& Watkins, K.E. (2014). Exploring the use of
egocentric online social network data to characterize individual air travel
behavior. \textit{ Transportation Research Record}, 2400, 78–86.
\url{https://doi.org/10.3141/2400-09} \ifdetail \textbf{Citations: 15}  \fi

  \item McBride, J.H., Keach, R. W., Macfarlane, R.T., De Simone, G.F., Scarpati, C.,
Johnson, D.J., \textbf{Macfarlane, G.S.}, \& Weight, R.W.R. (2009). Subsurface visualization using
ground-penetrating radar for archaeological site preparation on the northern
slope of Somma-Vesuvius: a Roman site, Pollena-Trocchia, Italy. \textit{ Il Quaternario,
Italian Journal of Quaternary Sciences}, 22(1), 39–52. \url{https://portal.issn.org/resource/ISSN/0394-3356} 
\end{myenum}

\ifdetail
\section{Venue Notes}
I publish in a wide variety of journals, including both traditional and open-access journals. 
The description of each journal includes Scopus CiteScore and relative ranking in the most
relevant field; Clarivate Impact Factor, and Scimago journal quartile ranking. 

\begin{description}
  % get impact factor data from https://jcr.clarivate.com/jcr-cj/my-favorites
  % get cite score data from https://www.scopus.com/list/form/overview.uri?listTypeValue=Sources
  % get scimago data from 
  \item[\textit{Transportation Research Part C: Emerging Technologies}] is a
  leading international journal with robust peer review focusing on applications
  and implications of technology in transportation systems.
  CiteScore: 15.9; 9/407 in civil engineering.  Impact Factor: 7.9. Scimago: Q1. Publisher: Elsevier.
  \item[\textit{Transportation Research Part A: Policy and Practice}] is
   a leading international journal with robust peer review focusing on
   transportation policy  analysis and the planning of transportation systems.
   CiteScore: 11.3; 27/407 in civil engineering. Impact Factor: 6.8. Scimago: Q1. Publisher: Elsevier.
  \item[\textit{Smart Cities}] is an international, scientific, peer-reviewed,
  open access journal on the science and technology of smart cities. CiteScore:
  14.7, 4/288 in urban studies. Impact Factor: 5.5. Scimago: Q1. Publisher: MDPI.
  \item[\textit{Journal of the American Planning Association}] is the quarterly
  journal of record for the planning profession. CiteScore: 7.3, 20/288 in urban studies. 
  Impact Factor: 3.4. Scimago: Q1.  Publisher: Taylor \& Francis.
  \item[\textit{Environment and Planning B: Urban Analytics and City Science}]
  is a leading international journal with robust peer review publishing
  cutting-edge research in analytical methods for urban planning and
  design. CiteScore 7.3; 21/288 in urban studies. Impact Factor: 3.1. Scimago: Q1. Publisher: Sage.
  \item[\textit{Journal of Transport \& Health}] is an international, peer reviewed journal devoted to publishing research that advances knowledge on the many interactions between transport and health and the policies that affect these. CiteScore: 6.3, 13/109 in safety research. Impact Factor: 3.3. Scimago: Q1. Publisher: Elsevier.
  \item[\textit{Journal of Transport and Land Use}] is the leading
  international journal that publishes original interdisciplinary papers on the
  interaction of transport and land use. CiteScore: 4.0; 67/279 in urban
  studies. Impact Factor: 2.2. Scimago: Q1. Publisher: University of Minnesota.
  \item[\textit{International Journal of Environmental Research and Public Health}]
  is an interdisciplinary, open access journal with peer review. CiteScore: 7.3;
  104/665 in public health. Impact Factor: 8.5. Scimago: Q2. Publisher: MDPI.
  \item[\textit{Journal of Transportation Engineering Part A: Systems}] contains
  technical and professional engineering articles with robust peer review on the
  planning, design, construction, operation, and maintenance of air, highway,
  rail, and urban transportation systems and infrastructure.  CiteScore: 4.0;
  157/407 in civil engineering. Impact Factor: 2.1. Scimago: Q2. Publisher: ASCE.
  \item[\textit{Transportation Research Record}] is the Journal of the
  Transportation Research Board of the National Academies. Since 2020, the 
  journal has undergone a transformation to institute more rigorous peer review.
  CiteScore: 3.4; 178/407 in civil engineering. Impact Factor: 2.1. Scimago: Q2. Publisher: Sage.
  \item[\textit{Future Transportation}] is an international, peer-reviewed, open
  access journal on the civil engineering, economics, environment and geography,
  computer science and other transdisciplinary dimensions of transportation. 
  CiteScore: 3.8; 92/264 in engineering (miscellaneous). Impact Factor: 1.7. Publisher: MDPI.
  \item[\textit{Findings}] is an interdisciplinary, independent, community-led,
  peer-reviewed, open access journal focused on short, clear, and pointed
  research results. This is a unique journal with short papers and fast peer review
  focused on quickly disseminating important transportation science. Though it is a
  non-traditional journal, some of the most important names in my field have 
  published here and I support the efforts of the transportation community to
  move to new forms of scientific publishing.
  Scimago: Q2. Publisher: University of Sydney and McGill University.
\end{description}
\fi

% \textbf{Macfarlane, G.S.}, \& Lant, N.$^\dagger$ (2021). Identifying Segmentation Strategies in a Daily Activity Pattern Model for Wheelchair Users.

\section{Peer- Reviewed Conference \\ Papers}
All listed conference papers are full papers and include at least a
single-blind review process with multiple expert reviewers for consideration.
This includes presentations at conferences where the requirement for submission is a full paper
with peer review, some of which do not publish an indexed proceeedings.
\ifdetail Papers 1 and 2 resulted from my undergraduate honors thesis, papers 3 through 5 work completed in graduate school, and subsequent work since joining the faculty at BYU. The marking $^\dagger$indicates BYU graduate student authors, $^*$indicates BYU undergraduate authors.\fi
\vspace{.3cm}
\begin{myenum}[13]
  \ifdetail{\color{NavyBlue} \fi
  \item Hyer, J.C.$^\dagger$, Schultz, G.G., \textbf{Macfarlane, G.S.} (2025). An analysis
  of UDOT’s expanded incident management team program. In \textit{International Conference on Transportation \& Development (ICTD 2025)}. ASCE. \url{https://doi.org/10.1061/9780784486207.037} 

  \item Atchley, S.H.$^\dagger$, Mansfield, K.A.$^*$, \textbf{Macfarlane, G.S.}
  (2025). A comparative illustration of trip- and activity-based modeling
  methods. In \textit{International Conference on Transportation \& Development (ICTD 2025)}. ASCE. \url{https://doi.org/10.1061/9780784486207.002}

\item Jarvis, D.L.$^\dagger$, \textbf{Macfarlane, G.S.}, Woolley, B.$^*$,
Schultz, G.G. (2024). Simulating incident management team response and
performance. \textit{Procedia Computer Science}. 238,
pp. 91-96.
\url{https://doi.org/10.1016/j.procs.2024.06.002}

\item Apelu, D.$^*$, \textbf{Macfarlane, G.S.}, Guthrie, W.S., Adams, N.$^*$,
Mazzeo, B. (2023). Measuring Pavement Smoothness From the Perspective of
E-Scooters. \textit{IEEE XPlore},
\url{https://doi.org/10.1109/IETC57902.2023.10152077}

\item \textbf{Macfarlane, G.S.}, Lant, N.$\dagger$ (2023). How Far Are We From Transportation Equity? Measuring the Effect of Wheelchair Use on Daily Activity Patterns. In: Antoniou, C., Busch, F., Rau, A., Hariharan, M. (eds) Proceedings of the 12th International Scientific Conference on Mobility and Transport. \textit{Lecture Notes in Mobility.} Springer, Singapore. \url{https://doi.org/10.1007/978-981-19-8361-0_10}
\ifdetail } \fi

\item Voulgaris, C.T., \textbf{Macfarlane, G.S.}, Kaylor, J., Su, T., Bauranov, A. (2022). Whose emissions are these anyway? Estimating vehicle miles traveled to account for site-level climate impacts. In \textit{Transportation Research Board Annual Meeting}. Washington, D.C.
\item \textbf{Macfarlane, G.S.}, Stucki,  E.$^\dagger$,  \& Copley, M.$^*$. (2021). Utility-Based Accessibility to Community Resources: An Application of Location-Based Services Data. In \textit{North American Regional Science Conference}. Denver, Colorado.
\item \textbf{Macfarlane, G.S.}, \& Tapia, T. (2020). Developing a Park Activity Location Choice Model from Passive Origin-Destination Data Tables. In \textit{ Transportation Research Board Annual Meeting}. Washington, D.C.
\item \textbf{Macfarlane, G.S.}, \& Moreno-Cruz, J. (2015). The Association Between Public Transportation Infrastructure and Home Price Growth and Stability. \textit{North American Regional Science Conference}. Portland, Oregon.
\item Zhang, B., \textbf{Macfarlane, G.S.}, Wall, T.A., \& Watkins, K.E. (2014). Friendship Influences on Air Travel: A Social Autoregressive Analysis. In \textit{ North American Regional Science Conference}. Washington, D.C.
\item \textbf{Macfarlane, G.S.}, Moreno-Cruz, J., \& Garrow, L. A. (2013). Does Atlanta value MARTA? Selecting an autoregressive model to recover willingness-to-pay. In \textit{ North American Regional Science Conference}. Atlanta, Georgia.
\item \textbf{Macfarlane, G.S.}, Saito, M., \& Schultz, G.G. (2011). Delay underestimation at free right-turn channelized intersections. In \textit{ 6th
International Symposium on Highway Capacity and Quality of Service} (Vol. 16,
pp. 560–567). https://doi.org/10.1016/j.sbspro.2011.04.476 \ifdetail Citations:
6  \fi

\item \textbf{Macfarlane, G.S.}, Saito, M., \& Schultz, G.G. (2011). Driver
perceptions at free right-turn channelized intersections. In \textit{ T\&DI
Congress 2011: Integrated Transportation and Development for a Better Tomorrow} 
(Vol. 398, pp. 108–108). ASCE. https://doi.org/10.1061/41167(398)108 \ifdetail
Citations: 5  \fi
\end{myenum}


\section{Reports}
\ifdetail These are technical reports completed under contract for the sponsoring agency;
each report was reviewed by a technical advisory committee prior to publication. Item 1 
resulted from postdoctoral activities at Georgia Tech, 
items 2 and 3 from my consulting practice, and items 4 through the present from my work 
since joining BYU.\fi
\vspace{0.3cm}
\begin{myenum}[17]
  \ifdetail{\color{NavyBlue} \fi
\item \textbf{Macfarlane, G.S.}, Atchley, S.H.$^\dagger$, Mansfield, K.A.$^*$, Baird, T. \& Gresham, C. (2024). 
  \textit{Activity-based Model Implementation and Analysis Considerations. }  (No. UT-24.16).  Utah Dept.\ of Transportation. Division of Research. \url{https://rosap.ntl.bts.gov/view/dot/77610}

\item \textbf{Macfarlane, G.S.},  Jarvis, D.L.$^\dagger$, Woolley, B.$^*$, \& Schultz, G.G. (2024).
  \textit{Simulating Incident Management Team Response and Performance.} (No. UT-23.22). 
  Utah Dept.\ of Transportation. Division of Research. \url{https://rosap.ntl.bts.gov/view/dot/74034}

\item \textbf{Macfarlane, G.S.}, Stucki, E.$^\dagger$, Redelfs, A.H., Spruance, L.A. (2023). 
  \textit{Equitable Access to Nutrition in Utah}  (No. UT-23.23).  Utah Dept.\ of Transportation. Division of Research. \url{https://drive.google.com/file/d/1n1wK_9PtFW9l1ytaDEfJhzG2mr5ws0Bw}

\item Schultz, G.G., Hyer, J.$^\dagger$, Holdsworth, H.$^*$, Eggett, D.L., \& \textbf{Macfarlane, G.S.} (2023).
  \textit{Analysis of Benefits of UDOT’s Expanded Incident Management Team Program.} (No. UT-23.05). 
  Utah Dept.\ of Transportation. Division of Research. \url{https://doi.org/10.21949/1528563} 

  \item  \textbf{Macfarlane, G.S.}, Atchley, S.H.$^\dagger$ (2023).
  \textit{Identifying Microtransit Service Areas through Microsimulation}. 
  (No. UT-23.01). Utah Dept.\ of Transportation. Division of Research.
  \url{https://rosap.ntl.bts.gov/view/dot/66312}

\item Guan, H.Z., Van Hentenryck, P., Goyal, V., Hoque, J., Day, C.S., \textbf{Macfarlane, G.S.}, Erhardt, G.D., Watkins, K.E. (2023). \textit{T-SCORE Project M1---- Multi-Modal Optimization: Development of Optimization Frameworks on On-demand Multimodal Transit Systems}.  Transit-Serving Communities Optimally, Responsively, and Efficiently Center (T-SCORE); Office of the Assistant Secretary for Research and Technology.  \url{https://trid.trb.org/view/2320639}

\item Tenenboim, E., Xu, Y.,  \textbf{Macfarlane, G.S.},  Erhardt, G.D., Peeta, S. \textit{T-SCORE Project M2 --- Multi-Agent Simulation: A Model of Ride-Hailing Driver Participation}.  Transit-Serving Communities Optimally, Responsively, and Efficiently Center (T-SCORE); Office of the Assistant Secretary for Research and Technology. \url{https://trid.trb.org/view/2320640}

\item Day, C.S., \textbf{Macfarlane, G.S.}, Erhardt, G.D., Watkins, K.E. (2023). \textit{T-SCORE Projects M3 --- MMOS Integration: Forecasting Ride-Hailing Across Multiple Model Frameworks.} Transit-Serving Communities Optimally, Responsively, and Efficiently Center (T-SCORE); Office of the Assistant Secretary for Research and Technology. \url{https://trid.trb.org/view/2149944}

\item Erhardt, G.D., \textbf{Macfarlane, G.S.}, Atchley, S.A. Lant, N., Mucci, R.A., Watkins, K.E. (2023). \textit{T-SCORE Project M4 --- Implementation and Quantitative Evaluation: Case Studies on Microtransit and Ride-Hailing}. Transit-Serving Communities Optimally, Responsively, and Efficiently Center (T-SCORE); Office of the Assistant Secretary for Research and Technology. \url{https://trid.trb.org/view/2320637}


\item Schultz, G.G. \textbf{Macfarlane, G.S.}, Wang, B.$^\dagger$, \& Davis,
  M.C.$^*$ (2022). \textit{Detecting Traffic Data Anomalies in Longitudinal Signal
  Performance Measures}. (No. UT-22.21). Utah Dept.\ of Transportation. Division of
  Research. \url{https://rosap.ntl.bts.gov/view/dot/65833}

\item Schultz, G. G., \textbf{Macfarlane, G.S.}, Daines, T.J.$^\dagger$, Ward,
  C.K.$^*$, Umphress, J.$^*$ (2022). \textit{Evaluating Ramp Meter Wait Time in
  Utah}. (No. UT-21.06). Utah Dept.\ of Transportation. Division of Research.
  \url{https://rosap.ntl.bts.gov/view/dot/61507}
  \ifdetail } \fi

\item \textbf{Macfarlane, G.S.}, Lant, N.J.$^\dagger$, (2021).
  \textit{Estimation and Simulation of Daily Activity Patterns for Individuals
  Using Wheelchairs} (No. UT-21.10). Utah Dept.\ of Transportation. Division of
  Research. \url{https://rosap.ntl.bts.gov/view/dot/54639/dot_54639_DS1.pdf}

\item Schultz, G. G., \textbf{Macfarlane, G.S.}, Wang, B.$^\dagger$, \& McCuen,
  S.$^*$ (2020). \textit{Evaluating the Quality of Signal Operations Using Signal
  Performance Measures} (No. UT-20.08). Utah Dept.\ of Transportation. Division of
  Research. \url{https://rosap.ntl.bts.gov/view/dot/54639/dot_54639_DS1.pdf}

\item \textbf{Macfarlane, G.S.} \& Copley, M.J.$^*$ (2020). \textit{ A Synthesis
  of Passive Third-Party Data sets used for Transportation Planning.} (No.
  UT-20.20). Utah Dept.\ of Transportation. Division of Research.
  \url{https://rosap.ntl.bts.gov/view/dot/54890/dot_54890_DS1.pdf}

\item Zalewski, A., Sonenklar, D., Cohen, A., Kressner, J., \&
  \textbf{Macfarlane, G.S.} (2019). \textit{ Public Transit Rider
  Origin–Destination Survey Methods and Technologies}. TCRP Synthesis of Transit
  Practice 138. Transportation Research Board.
  \url{http://www.trb.org/Main/Blurbs/179008.aspx} \ifdetail Citations: 1  \fi

\item Miller, H., O'Kelly, M., Jaegal, Y., Bachman, W., Huntsinger, L., \&
  \textbf{Macfarlane, G.S.} (2017). \textit{Estimating External Travel Using
  Purchased Third-Party Data.} Research Report 134877, the Ohio Department of
  Transportation, Office of Statewide Planning \& Research. \ifdetail Citations: 1 \fi

\item Cruz, J., \textbf{Macfarlane, G.S.}, Xu, Y., Rodgers, M.O., \& Guensler,
  R. (2015). \textit{Sustainable Transportation Curricula}. National Center for
  Sustainable Transportation. \url{https://escholarship.org/uc/item/3c13q43c}.
\end{myenum}


\section{Conferences Organized}
\ifdetail
This includes conferences and symposia for which I served on an organizing or
scientific committee.
\fi
\vspace{0.3cm}

\begin{myenum}[1]
  \ifdetail{\color{NavyBlue} \fi
  \item{\textit{Activity-based Modeling Symposium} (2024). M\"ockel, R. (host),
  Shaw, A., Bhat, C.R., Erhardt, G.D.,  \textbf{Macfarlane, G.S.}, \&
  Mokhtarian, P.L., scientific committee.   Hosted in Raitenhaslach, Germany
  with funding from the German Research Foundation.
  \url{https://www.mos.ed.tum.de/en/tb/workshops/abm2024/}}
  \ifdetail} \fi
\end{myenum}  

\section{Presentations}
\ifdetail This includes invited presentations to academic and non-academic audiences, as
well as presentations resulting from abstract-only submission. Includes both
lectern sessions and posters. Item 1 came from my undergraduate honors thesis, items 2 through 4 from doctoral research,
items 5 through 10 from my work as a consultant, and items 11 through the present represent work
completed during my time at BYU.\fi
\vspace{0.3cm}

\begin{myenum}[43]
  \ifdetail{\color{NavyBlue} \fi
\item \textbf{Macfarlane, G.S.} (2025). Travel behavior and access to opportunity. In the \textit{For the Benefit of the World Conference}. Poster; Provo, Utah.
\item \textbf{Macfarlane, G.S.}, Christesen, E.$\dagger$, Chandler, C.$^*$, Erhardt, G.D., Watkins, K.E. (2025). California HSR model transferability. In \textit{CalTrans Transit Research to Practice Symposium}. Online webinar.
\item \textbf{Macfarlane, G.S.}, Asmussen, K., Schiffer, R., Swim, S., Vyas, G. (2025). Anticipating the future of travel forecasting practice. In \textit{Modeling Mobility Conference}. University of Minnesota. Moderator for opening plenary panel. Minneapolis, Minnesota.
\item Admundsen, H., Stathopoulous, A., \textbf{Macfarlane, G.S.}, Handy, S., Ory, D. (2025). Induced demand is hogwash. In \textit{Modeling Mobility Conference}. University of Minnesota. Invited participant in moderated debate. Minneapolis, Minnesota.
\item Lu, R., Ji, J.Y., Wang, L.M., Belkessa, L., Dong, Y., Madadi, B., Varotto, S., Saunier, N., \textbf{Macfarlane, G.S.}, Ghosh, B., Ameli, M., \& Wu, C. (2025).  Towards accelerating transportation research: Measuring the state of transparency practices. In \textit{Transportation Research Symposium}, Elsevier. Lectern presentation. Rotterdam, Netherlands.
\item South, A.,  \textbf{Macfarlane, G.S.} (2025) Sustainable community development. BYU Masters of Public Administration -- Mongolian government exchange program, Marriott School of Business. Invited lecture. Provo, Utah.
\item \textbf{Macfarlane, G.S.}. (2025) The potential for transit to improve access to quality nutrition. In \textit{ITS Graduate Seminar}. University of California, Davis Institute of Transportation Studies. Invited lecture. Davis, California.
\item \textbf{Macfarlane, G.S.}, Sheffield, M.$^\dagger$, Bennett, L.$^\dagger$ and Schultz, G.G. (2025). Signal Priority on BRT Lines in Provo, Utah. In \textit{4th Annual Transit Research Symposium}. University of California, Davis Institute of Transportation Studies. Lectern presentation. Davis, California.
\item \textbf{Macfarlane, G.S.} (2024). A multiple modeling sandbox. In \textit{Activity-based models symposium}. Technische Universit\"at M\"unchen. Lectern presentation. Raitenhaslach, Germany.
\item Lawe, S. \& \textbf{Macfarlane, G.S.} (2024). Why travel forecasting is more complex and more important than ever before. In \textit{Utah Transportation Conference}. Lectern presentation, Sandy, Utah.
\item \textbf{Macfarlane, G.S.}, Baird, T., \& Atchley, S.H.$^\dagger$ (2024). Activity-based models in Utah: A comparative illustration. In \textit{Utah Model User's Group Meeting}. Working group presentation. Orem, Utah. 
\item Voulgaris, C.T., Jensen, A.F., \textbf{Macfarlane, G.S.} (2024). Children’s mode choice and independence for the journey to school. In \textit{17th International Conference on Travel Behavior Research}. Lectern presentation. Vienna, Austria.
\item Baird, T., Gresham, C., Atchley, S.H.$^\dagger$ \& \textbf{Macfarlane, G.S.} (2024). A Clearer Crystal Ball? Practitioner perspectives on improving travel models. In \textit{Mountain District ITE Meeting}. Lectern presentation. Big Sky, Montana. 
\item Jarvis, D.L.$^\dagger$, \textbf{Macfarlane, G.S.}, Woolley, B.$^*$, Schultz, G.G. (2024). Simulating incident management team response and performance. In \textit{The 15th International Conference on Ambient Systems, Networks and Technologies (ANT)}. Hasselt, Belgium. Lectern presentation.
\item \textbf{Macfarlane, G.S.}, Barnes, M.$^\dagger$, \& Gray, N.M.$^*$ (2024).  A utility-based approach to modeling systemic resilience of highway networks with an application in Utah.  In \textit{Transportation Research Board Annual Meeting}. Poster presentation. Washington, D.C.
\item Brown, N., \textbf{Macfarlane, G.S.}., Baird, T., \& Gresham, C. (2023). Activity-based models: A clearer crystal ball? in \textit{Utah Transportation Conference}. Lectern presentation. Sandy, Utah.
\item \textbf{Macfarlane, G.S.} Modeling with Big Data. (2023) At \textit{Technische Universit\"at M\"unchen}, invited lecture in Dr. Rolf M\"ockel's travel modeling course. Munich, Germany.
\item Guan, H.Z., Van Hentenryck, P., Erhardt, G.D., \textbf{Macfarlane, G.S.}, \& Watkins, K.E. (2023). Lessons from the design of on-demand multimodal transit systems in two cities. In \textit{Innovations in Transportation Analysis and Planning Conference}. Lectern presentation. Indianapolis, Indiana. \textit{Winner, best presentation by a student author.}
\item Ducuara, A. Holtrop-Kohl, L., Begay, S., Spruance, L., Redelfs, A., \textbf{Macfarlane, G.S.} (2023). Hungry for change: how cutting-edge research is helping to reduce food deserts in Utah. In \textit{Move Utah Summit}. Moderated panel discussion. Salt Lake City, Utah.
\item Singh, G., Young, S., \textbf{Macfarlane, G.S.}, Katsikides, N., Granato, S. (2023). Travel Data Users Forum: Innovative Usage of GPS Trajectory Data: Present and Future. In \textit{Transportation Research Board Annual Meeting}. Invited panel discussion. Washington, D.C.
\item \textbf{Macfarlane, G.S.}, Barnes, M.$^\dagger$, \& Gray, N.$^\dagger$. (2022). Evaluating systemic resiliency in Utah. In \textit{Utah Dept. of Transportation Annual Conference}. Lectern presentation. Sandy, Utah.
\item \textbf{Macfarlane, G.S.}, Day, C.S.$^\dagger$, \& Atchley, S.H.$^\dagger$. (2022). Modeling novel transport modes. In \textit{Utah Dept. of Transportation Annual Conference}. Lectern presentation. Sandy, Utah.
\item Antoniou, C., M\"ockel, R., \textbf{Macfarlane, G.S.}, Kotsopoulous, H., Llorca-Garcia, C., Erhardt, G.D., Mahajan, V.,  Schm\"ocker, J.D., \& Pereira, F. (2022). Transport Modeling using Publicly Available Data. Invited participants to a workshop hosted by Technische Universit\"at M\"unchen and the German Research Foundation.
\item \textbf{Macfarlane, G.S.}, \& Lant, N.J.$^\dagger$ (2022). How far are we from transportation equity? Measuring the effect of wheelchair use on daily activity patterns. In \textit{mobil.TUM 2022 – 12th International Scientific Conference on Mobility and Transport}. Lectern presentation. Singapore.
\item \textbf{Macfarlane, G.S.}, \& Atchley, S.H.$^*$, Day, C.S.$^\dagger$, Erhardt, G., \& Needell, Z. (2022). Simulating and prioritizing service areas for regionally exclusive microtransit operations. In \textit{mobil.TUM 2022 – 12th International Scientific Conference on Mobility and Transport}. Lectern presentation. Singapore.
 \ifdetail } \fi
\item Anderson, S.$^*$, \textbf{Macfarlane, G.S.}, \& Schultz, G.G. (2022). Developing a New Method to Analyze Speed and Braking Data Using V2X Technology. In \textit{Utah Conference of Undergraduate Research}. Poster. St.\ George, Utah.
\item \textbf{Macfarlane, G.S.} (2022). Using Big Data to Evaluate Equitable Access to Community Resources. In \textit{Transportation Research Board Annual Meeting}. Invited lectern presentation. Washington, D.C.
\item \textbf{Macfarlane, G.S.}, Stucki,  E.$^\dagger$,  \& Copley, M.$^*$. (2021). Utility-Based Accessibility to Community Resources: An Application of Location-Based Services Data. In \textit{North American Regional Science Conference}. Denver, Colorado.
\item \textbf{Macfarlane, G.S.}, Lant, N.J.$^\dagger$, (2021). Estimation and Simulation of Daily Activity Patterns for Individuals Using Wheelchairs. In \textit{Utah Dept. of Transportation Annual Conference.} Lectern presentation. Sandy, Utah.
\item \textbf{Macfarlane, G.S.} \& Copley, M.J.$^*$ (2020).  A Synthesis of Passive Third-Party Data sets used for Transportation Planning. In \textit{Utah Dept. of Transportation Annual Conference}. Poster. Sandy, Utah.
\item Voulgaris, C.T., \textbf{Macfarlane, G.S.}, Kaylor, J., Su, T., Bauranov, A. (2021). Whose emissions are these anyway? Estimating vehicle miles traveled to account for site-level climate impacts. In \textit{Association of Collegiate Schools of Planning Annual Conference}. Lectern presentation. Miami, Florida.
\item \textbf{Macfarlane, G.S.}, Boyd, N., Taylor, J.E., \& Watkins, K.E. (2019). Modeling the impacts of park access on health outcomes: a choice-based accessibility approach. In \textit{Greater and Greener 2019}. Workshop presentation. Denver, Colorado.
\item Bernardin, V., Gallup, A., Lee, B., Johnson, C., \textbf{Macfarlane, G.S.}, Elgar, I., Wertman, R. (2019). How to be a Good Big Data Consumer. In \textit{Transportation Planning Applications Conference}. Panel discussion. Portland, Oregon.
\item \textbf{Macfarlane, G.S.}, \& Kressner, J.D. (2018). Comparing the Daily Schedules in the NHTS from 2009 and 2017. In \textit{National Household Travel Survey (NHTS) Data for Transportation Applications Workshop}. Poster. Washington, D.C.
\item \textbf{Macfarlane, G.S.}, Bettinardi, A.O., \& Donnelly, R. (2017). SWIMR: Visualizing complex longitudinal indicators for a statewide integrated land use and transport model in Oregon. In \textit{Transportation Planning Applications Conference}. Lectern presentation. Raleigh, North Carolina.
\item Boyd, N., \textbf{Macfarlane, G.S.}, Watkins, K.E., \& Ederer, D. (2017). Accessibility to urban parks and health outcomes on the neighborhood level. In \textit{ American Public Health Association Annual Meeting}. Poster. Atlanta, Georgia.
\item \textbf{Macfarlane, G.S.}, \& Kressner, J.D. (2017). Modeling automated vehicles with a passive data model. In \textit{Transportation Planning Applications Conference}. Poster. Raleigh, North Carolina.
\item Kressner, J.D., \textbf{Macfarlane, G.S.}, Donnelly, R., \& Huntsinger, L.F. (2016). Using passive data to build an agile tour-based model: A case study in Asheville. In \textit{Innovations in Travel Modeling Conference}. Lectern presentation. Denver, Colorado. \ifdetail Citations: 7  \fi
\item \textbf{Macfarlane, G.S.}, \& Kressner, J. D. (2016). Fusing Passive Data for Transportation Planning. In \textit{Transportation Research Board Annual Meeting}. Poster. Washington, D.C.
\item \textbf{Macfarlane, G.S.}, \& Moreno-Cruz, J. (2015). The association between public transportation infrastructure and home price growth and stability. \textit{In Transportation Research Board Annual Meeting}. Washington, D.C.
\item \textbf{Macfarlane, G.S.}, \& Garrow, L. A. (2012). Estimating a vehicle ownership model from targeted marketing data. In \textit{Travel Surveys: Moving from Tradition to Practical Innovation}. Poster. Dallas, Texas.
\item Kressner, J.D., \& \textbf{Macfarlane}, G.S. (2012). Evaluating household credit reports as a replacement for episodic travel surveys. In \textit{Transportation Research Board Annual Meeting}. Committee presentation. Washington, D.C.
\item \textbf{Macfarlane, G.S.}, Saito, M., \& Schultz, G.G. (2011). Are free right-turn channelized intersections performing as they should? In \textit{Institute of Transportation Engineers Annual Meeting and Exhibit 2011}.
\end{myenum}



%% ==========================================
\section{External \\Funding}

As Principal Investigator, totalling \$503,000:
\vspace{0.3cm}
\begin{myenum}[9]
  \ifdetail {\color{NavyBlue} \fi
  \item {\textbf{Macfarlane, G.S.} \& Atchley, S.H. 2025. \textit{Establishing Performance Measures for Transportation and Quality of Life}. \$68,000, Utah Department of Transportation.}
  \item {\textbf{Macfarlane, G.S.} \& Schultz, G.G. 2024. \textit{Effectiveness of Temporary Portable Rumble Strips}. \$60,000, Utah Department of Transportation.}
  \item {\textbf{Macfarlane, G.S.} \& Brown, N.M. 2022. \textit{Activity-based Model Implementation and Analysis Considerations}. \$70,000, Utah Department of Transportation.}
  \ifdetail } \fi
  \item {\textbf{Macfarlane, G.S.} \& Schultz, G.G. 2021. \textit{Optimizing Traffic Incident Management Deployment in Utah}. \$70,000, Utah Department of Transportation.}
  \item {\textbf{Macfarlane, G.S.}, Redelfs, A.H., \& Spruance, L.A. 2021. \textit{Equitable Access to Nutrition in Utah}. \$70,000, Utah Department of Transportation.}
  \item {\textbf{Macfarlane, G.S.} 2020. \textit{ Identifying Microtransit Service Areas
through Microsimulation}. \$20,000, Utah Department of Transportation.}
  \item {\textbf{Macfarlane, G.S.} 2019. \textit{ A synthesis of passive third-party datasets
used for transportation planning}. \$25,000, Utah Department of Transportation}
  \item {\textbf{Macfarlane, G.S.} 2019. \textit{ Modeling the demand and operating
characteristics for wheelchair-accessible, on-demand mobility services}.
\$60,000, Utah Department of Transportation}
  \item {\textbf{Macfarlane, G.S.} 2019. \textit{ Evaluating the Systemic Redundancy of
Critical Highway Facilities}. \$60,000, Utah Department of Transportation}
\end{myenum}

As Co-Principal Investigator, totalling \$1.44 million (\$320,000 to BYU):
\vspace{0.3cm}
\begin{myenum}[5]
  \ifdetail {\color{NavyBlue} \fi
  \item{Watkins, K.E. (PI), Erhardt, G.D., \& \textbf{Macfarlane, G.S.} 2024. \textit{The Potential for Behavioral Change in New High Speed Rail Lines}. \$280,000, California High Speed Rail Authority and Deutsche Bahn.}
  \ifdetail } \fi
  \item{Schultz, G.G. \& \textbf{Macfarlane, G.S.}. 2021. \textit{Analysis of
  performance measures of UDOT’s traffic incident management program: Phase
  III}. \$30,000. Utah Department of Transportation.}
  \item{Watkins, K.E. (PI), Hunter, M.S., Van Hentenryck, P., Peeta, S.,
  Brakewood, C., Cherry, C., Erhardt, G.D., \& \textbf{Macfarlane, G.S.} 2020. \textit{
  T-SCORE: Transit Serving Communities Optimally, Responsibly, and Efficiently}.
  \$1,000,000, United States Department of Transportation.}
  \item{ Schultz, G.G. (PI), \textbf{Macfarlane, G.S.} 2020. \textit{ Evaluating Signal
  Performance Measures: a Longitudinal Analysis}. \$70,000, Utah Department of
  Transportation}
  \item{ Schultz, G.G. (PI), \textbf{Macfarlane, G.S.} 2019. \textit{ Evaluating ramp meter
delay in Utah}. \$65,000, Utah Department of Transportation}
\end{myenum}

\ifdetail
Unfunded Proposals:
\vspace{0.3cm}
\begin{myenum}[3]
  \ifdetail {\color{NavyBlue} \fi
  \item{Dashti, S. (PI), Torres-Machi, C., Mooney, M., Misra, A., Crow, D., Mallet, S., Esteghemati, M, \textbf{Macfarlane, G.S.}, Zlatkovic, M., Kack, D. (2023). \textit{Resilient, Equitable, and Sustainable Environment through Transportation (RESET)}. \$3,000,000. United States Department of Transportation.}
  \item{Erhardt, G.D. (PI), Watkins, K.E., Brakewood, C.,  Pike, S.C., \textbf{Macfarlane, G.S.}, Chavis, C., Tal, G., Hunter, M., Van Hentenryck, P., McDonald, N. (2022). \textit{T-SCORE 2.0: Transit – Sustainable, Competitive, Responsive, and Equitable Center}. \$2,000,000. United States Department of Transportation.}
  \item{Voulgaris, C.T. (PI), Forsyth, A., Pandey, V., Park, H., Handy, S., \textbf{Macfarlane, G.S.}, Pande, A., Braun, L.M., Noland, R.B. (2023). \textit{Chester: Consortium for Healthy, Equitable, and Sustainable Transportation Systems for Environmental Resilience}. \$2,000,000, United States Department of Transportation}
  \ifdetail } \fi
\end{myenum}
Pending Proposals:
%\begin{myenum}[0]
%\end{myenum}

\fi
\section{Internal Competitive Funding}
Funded research:
\begin{itemize}
  \item {Sowby, R.B. \& \textbf{Macfarlane, G.S.} (2024). \textit{Wildfire Solutions for Western Water Utilities}. \$25,000, Mentored Research Grant, Brigham Young University.}
  \item {\textbf{Macfarlane, G.S.}, Guthrie, W.S., \& Mazzeo, B. (2021). \textit{ Measuring pavement smoothness from the perspective of e-scooters}. \$25,000, Mentored Research Grant, Brigham Young University.}
\end{itemize}

\ifdetail
Unfunded proposals:
\begin{itemize}
  \item{\textbf{Macfarlane, G.S.}, Hooley, C., Redelfs, A., South, M. 2020 \textit{ Using Mobile Device Data to Measure Isolation and Mental Health}}.
  \$40,000, Brigham Young University Interdisciplinary Research Grant.
\end{itemize}
\fi

%% ============================================================================
\section{Courses}

{\acc CCE 102: Sustainable Infrastructure}

\vspace{-.4cm}
Sustainability in built environments and infrastructure with a focus on global challenges and solutions.
 Converted from CCE 201 in Fall 2024.


\ifdetail
\begin{tabular}{*{4}{>{\rowfonttype}c}<{\rowfont{}}}
  \toprule
  Semester & Enrolled & Student Rating (Historical) & Average GPA\\
  \midrule
  Fall 2020 & 33 & 4.1--4.7 (4.1)& 3.41 \\
  Fall 2021 & 64 & 4.1--4.5 (4.3)& 3.25 \\
  \rowcolor{White}\rowfont{\color{NavyBlue}} Fall 2022 & 60 & 3.6--4.2 (4.3)& 3.26 \\
  \rowcolor{White}\rowfont{\color{NavyBlue}} Fall 2023 & 59 & 3.9--4.3 (4.2) & 3.24\\
  \rowcolor{White}\rowfont{\color{NavyBlue}} Spring 2024 (Study Abroad) & 20 & 3.9--4.9 (4.2) & 3.32\\
  \rowcolor{White}\rowfont{\color{NavyBlue}} Fall 2024 (Section 1) & 58 & 3.4--4.0 (3.5) & 3.53\\
  \rowcolor{White}\rowfont{\color{NavyBlue}} Fall 2024 (Section 3) & 47 & 3.2--3.8 (3.5) & 2.96\\
  \rowcolor{White}\rowfont{\color{NavyBlue}} Winter 2025 (Section 1) & 61 & 3.7--4.3 (3.7) & 3.02\\
  \rowcolor{White}\rowfont{\color{NavyBlue}} Winter 2025 (Section 3) & 66 & 3.9--4.3 (3.7) & 3.24\\
  \rowcolor{White}\rowfont{\color{NavyBlue}} Fall 2025 & 65 & 3.9--4.3 (3.9) & 3.35\\
  \bottomrule
\end{tabular}

\fi

\vspace{.4cm}
{\acc CE 361: Introduction to Transportation Engineering}

\vspace{-.4cm}
Transportation systems characteristics, traffic engineering and operations,
transportation planning, geometric design, pavement design, transportation
safety, freight, public transport, sustainable transportation.

\ifdetail
\begin{tabular}{*{4}{>{\rowfonttype}c}<{\rowfont{}}}
  \toprule
  Semester & Enrolled & Student Rating (Historical) & Average GPA\\
  \midrule
  Winter 2020 & 42 & 4.4--4.8 (4.4) & 3.13 \\
  Winter 2021 & 38 & 4.1--4.7 (4.4) & 3.21 \\
  \rowcolor{White}\rowfont{\color{NavyBlue}} Winter 2022 & 42 & 3.9--4.5 (4.5) & 3.42 \\
  \rowcolor{White}\rowfont{\color{NavyBlue}} Winter 2023 & 37 & 4.2--4.6 (4.5) & 3.28 \\
  \rowcolor{White}\rowfont{\color{NavyBlue}} Winter 2024 & 43 & 3.9--4.5 (4.4) & 3.39 \\
  \rowcolor{White}\rowfont{\color{NavyBlue}} Fall 2025 & 43 & 4.4--4.8 (4.6) & 3.34 \\
  \bottomrule

\end{tabular}

\fi

\vspace{.4cm}
{\acc CE 565: Urban Transporation Planning}

\vspace{-.4cm}
Characteristics of urban transportation planning and decision making, intermodal
transportation, land-use transportation interrelationships, transportation
demand modeling, site impact analysis, sustainable transportation, and livable
cities.

\ifdetail
\begin{tabular}{*{4}{>{\rowfonttype}c}<{\rowfont{}}}
  \toprule
  Semester & Enrolled & Student Rating (Historical) & Average GPA\\
  \midrule
  Fall 2019 & 12 & 3.9--4.9 (4.4) & 3.41 \\
  Fall 2020 & 19 & 4.1--4.7 (4.4) & 3.46 \\
  Fall 2021 & 19 & 3.9--4.9 (4.4) & 3.63 \\
  \rowcolor{White}\rowfont{\color{NavyBlue}} Winter 2023& 14 & 4.4--5.0 (4.6) & 3.24 \\ 
  \rowcolor{White}\rowfont{\color{NavyBlue}} Winter 2024& 14 & 3.9--4.7 (4.5) & 3.03 \\ 
  \rowcolor{White}\rowfont{\color{NavyBlue}} Winter 2025& 10 & 4.2--5.0 (4.5) & 3.46 \\ 
  \bottomrule

\end{tabular}

\fi

\vspace{.4cm}
{\acc CE 594R: Data Science for Engineers}

\vspace{-.4cm}
A first-semester graduate course in programming and data science techniques:
literate programming in Markdown and LaTeX, version control with git, data
manipulation and visualization with R, object-oriented programming with Java.

\ifdetail
\begin{tabular}{*{4}{>{\rowfonttype}c}<{\rowfont{}}}
  \toprule
  Semester & Enrolled & Student Rating (Historical) & Average GPA\\
  \midrule
  Fall 2019 & 4 & 4.8--5.0 () & 3.85 \\
  Fall 2020 & 9 & 3.5--4.7 () & 3.81 \\
  Fall 2021 & 6 & 4.5--5.0 () & 3.68\\
  \bottomrule

\end{tabular}


\fi



\vspace{.4cm}
{\acc CE 662: Transport Simulation and Analysis}

\vspace{-.4cm}
An advanced graduate course in traffic flow theory and simulation. Topics
include shock wave analysis, discrete event simulation of queues and daily
activity pattern choices, car following models, and traffic simulation.
Laboratory assignments use MATSim and PTV Vissim simulation softwares.


\ifdetail
\begin{tabular}{*{4}{>{\rowfonttype}c}<{\rowfont{}}}
  \toprule
  Semester & Enrolled & Student Rating (Historical) & Average GPA\\
  \midrule
  Winter 2019 & 2 & 4.6 (4.3) & 3.70 \\
  Winter 2020 & 3 & 5.0--5.0 (4.4) & 3.00 \\
  \rowcolor{White}\rowfont{\color{NavyBlue}} Winter 2022 & 7 & 3.3--5.0 (4.3) & 3.44   \\
  \rowcolor{White}\rowfont{\color{NavyBlue}}Fall 2023 & 8 & 4.1--5.0 (4.4) & 3.48\\
  \bottomrule
\end{tabular}


\fi


\vspace{.4cm}
{\acc CE 694R: Advanced Choice Modeling}

\vspace{-.4cm}
An advanced graduate course in discrete choice modeling. Theory of choice
models, including estimation and validation techniques. Mode choice models for
work and non-work trip purposes using multinomial and nested logit models.

\ifdetail
\begin{tabular}{cccc}
  \toprule
  Semester & Enrolled & Student Rating (Historical) & Average GPA\\
  \midrule
  Winter 2021 & 5 & 4.0--5.0 () & 3.48 \\
  \bottomrule
\end{tabular}


\fi

% {\acc CEE 6622: Travel Demand Analysis}\hfill{Ga. Tech: Spring 2014}
%
% \vspace{-.4cm}
% This course teaches graduate students to develop and use urban travel
% demand models, including trip-based and activity-based modeling methods and
% experience with a modern practicing regional model.

%% ============================================================================
\section{Graduate Mentoring}
Students mentored as graduate committee chair (10 total, all MS):
\vspace{0.3cm}
\begin{myenum}[10]
  \ifdetail {\color{NavyBlue} \fi
  \item Erin Christesen. MS expected December 2026.
  \item Emily Youngs. \textit{Exploring the Link between Travel Behavior and Mental Health}. MS granted August 2024. Pursuing Ph.D. at University of Michigan.
  \item Hayden Atchley. \textit{A Comparative Illustration of Trip- and Activity-Based Modeling Techniques}. MS granted August 2024.
  \item Daniel Jarvis. \textit{Simulating Incident Management Team Response and Performance}. MS granted December 2023.
  \item Natalie Gray, \textit{Evaluating parameter uncertainty in transportation demand models}. MS granted June 2023.
  \item Emma Stucki, \textit{Evaluating equitable access to nutrition in Utah}. MS granted December 2022. Pursuing Ph.D. at Waikato University, New Zealand.
  \item Gillian Riches, \textit{Transforming GPS points to daily activities using simultaneously optimized DBSCAN-TE parameters}. MS granted December 2022.
  \item Christopher Day, \textit{Forecasting ride-hailing across multiple model frameworks.} MS granted December 2022.
  \ifdetail } \fi
  \item Max Barnes, \textit{Resiliency of Utah's road network: a logit-based approach.} MS granted December 2021.
  \item Nate Lant, \textit{Estimation and simulation of daily activity patterns for individuals using wheelchairs.} MS granted June 2021.
\end{myenum}

Students mentored as graduate committee member (22 total, 2 current, 3 non-BYU, 3 Ph.D.):
\vspace{0.3cm}
\begin{myenum}[22]
  \ifdetail {\color{NavyBlue} \fi
  \item Kendon Moline, MS expected December 2026
  \item Auzton Stutts, \textit{A Peer Evaluation of Safety at Signalized Intersections in Utah}. MS expected December 2026.
  \item Cambrie Ball. MS in Construction Management scheduled December 2025.
  \item Samuel McKinnon, Ph.D.\ in Mechanical Engineering pre-proposal.
  \item Adam W. Hill, \textit{Using unmanned aerial vehicles to facilitate traffic incident management}. MS granted April 2024.
  \item Ian MacGregor, \textit{Implementing the safe system approach at intersections in Utah}. MS granted December 2024.
  \item Sam Runyan, \textit{ Effect of roadway lighting on safety in Utah}. MS granted December 2024.
  \item Joel Hyer, \textit{Analysis of benefits of UDOT's expanded incident management team program.} MS granted April 2024.
  \item Matthew Davis, \textit{Effectiveness of intelligent transportation systems on Utah roadways}. MS granted December 2023.
  \item William Charlton, \textit{Web-based data visualization in support of agent-based microsimulation models}. Ph.D. granted October 2023 (at Technische Universit\"at Berlin).
  \item Wang Bangyu (Bruce), \textit{Evaluating and advancing automated traffic signal performance measures: Statistical and machine learning approaches}. Ph.D.\ granted August 2023.
  \item Tomas Barriga, \textit{Using severity weighted risk scores to prioritize safety funding in Utah}. MS granted August 2023.
  \item Benjamin Meek, \textit{Load-deformation behavior of tension-only X-brace roof truss diaphragms.} MS granted April 2023.
  \item Mylan Cook, \textit{Physics-guided modeling of acoustic environments using limited spatio-spectro-temporal data}. Ph.D.\ in Physics granted June 2023.
  \item Cory Ward, \textit{An evaluation of the safe speed limit setting procedure and tool for Utah} (Project). MS granted December 2022.
  \item Samantha Lau, \textit{Analysis of using V2X DSRC equipped snowplows to request signal preemption.} MS granted August 2022.
  \item Tanner Daines, \textit{Evaluating ramp meter delay in Utah}. MS granted April 2022.
  \ifdetail } \fi
  \item Logan Bennett, \textit{Analysis of benefits of an expansion to UDOT’s incident management program}. MS granted August 2021.
  \item Camille Lunt, \textit{Crash analysis methodology for segments of Utah highway}. MS granted April 2021.
  \item Chad Vickery, \textit{Quantifying the conditioning period for geogrid-reinforced aggregate base materials through cyclic loading}. MS granted August 2020.
  \item Michael Sheffield, \textit{Impacts of changing the transit signal priority requesting threshold on bus performance and general traffic: a sensitivity analysis}. MS granted June 2020.
  \item Michael Adamson, \textit{An analysis of decision boundaries for left-turn treatments}. MS granted April 2019.
  \item Nico Boyd, \textit{Accessibility to urban parks and health outcomes on the neighborhood level}. MS granted August 2018 (at Georgia Institute of Technology).
  \item Zhang Bingling, \textit{Friendship influences on air travel: a social autoregressive analysis}. MS granted August 2014 (at Georgia Institute of Technology).
\end{myenum}


\section{Undergraduate Mentoring}

Students mentored on funded research projects (28 total):
\vspace{0.2cm}
\begin{myenum}[30]
  \ifdetail {\color{NavyBlue} \fi
  \item Tyler Carruth, undergraduate research assistant in work zone safety (2024 - ).
  \item Benjamin Hailstone, undergraduate research assistant in work zone safety (2024 - ).
  \item Connor Williams, undergraduate research assistant in demand microsimulation (2024 - ).
  \item Kaleigh Squires, undergraduate research assistant in demand microsimulation (2024 - ).
  \item Kamryn Mansfield, undergraduate research assistant in demand microsimulation (2023 - 2024). Ph.D.\ student at University of Tennessee.
  \item Brynn Woolley, undergraduate research assistant in demand microsimulation (2022 - 2024). Ph.D.\ Student at University of Michigan.
  \item Jeremy Raine, undergraduate research assistant in community resources (2022). 
  \item Harrison Holdsworth, undergraduate research assistant in demand microsimulation (2021 - 2022). 
  \item Jonathan Orton, undergraduate research assistant in e-scooters and pavements (2022).
  \ifdetail } \fi
  \item Dylan Apelu, undergraduate research assistant in e-scooters and pavements (2021 - 2023). Completed MS at Georgia Institute of Technology.
  \item Matthew Davis, undergraduate assistant in signal performance data, jointly mentored with Grant Schultz (2021 - 2022). Ph.D.\ student at University of Tennessee.
  \item Hayden Atchley, undergraduate research assistant in demand microsimulation (2020 - 2022). Completed MS at BYU.
  \item Nicole Adams, undergraduate research assistant in e-scooters and pavements (2021 - 2022). 
  \item Liv Neeley, undergraduate research assistant in e-scooters and pavements (2021 - 2022). 
  \item Kaeli Monahan, undergraduate research assistant in community resources and passive data (2020 - 2022). 
  \item Shannon Anderson, undergraduate research assistant in V2X data, jointly mentored with Grant Schultz (2020 - 2022). 
  \item Corey Ward, undergraduate research assistant in ramp meter evaluation, jointly mentored with Grant Schultz (2020 - 2021). Completed MS at BYU.
  \item Michael Copley, undergraduate research assistant in third-party passive data (2018 - 2021). Completed MS at University of Illinois.
  \item James Umphress, undergraduate research assistant in ramp meters, jointly mentored with Grant Schultz (2020-2021). Completed MS at Oregon State University.
  \item Christopher Day, undergraduate research assistant in demand microsimulation (2020 - 2021). Completed MS at BYU.
  \item Emma Stucki, undergraduate research assistant in community resources (2020 - 2021). Completed MS at BYU.
  \item Gillian Martin Riches, undergraduate research assistant in community resources (2020 - 2021). Completed MS at BYU.
  \item Natalie Gray, undergraduate research assistant in network resiliency (2019 - 2021). Completed MS at BYU.
  \item Max Barnes, undergraduate research assistant in network resiliency (2019 - 2020). Completed MS at BYU.
  \item Kim Munseok, undergraduate research assistant in demand microsimulation (2020 - 2021). 
  \item Christian Hunter, undergraduate research assistant in demand microsimulation (2018 - 2019). Completed MS at University of Texas at Austin.
  \item Christian Vanderhoeven, undergraduate research assistant in demand microsimulation (2019). Completed MS at University of Washington.
  \item Hayden Anderson, undergraduate research assistant in e-scooters (2019 - 2020). Completed MS at University of California, Davis.
  \item Emily Andrus, undergraduate research assistant in signal peformance data, jointly mentored with Grant Schultz (2019). 
  \item Sabrina McCuen, undergraduate research assistant in signal peformance data, jointly mentored with Grant Schultz (2019 - 2020). 
\end{myenum}

Honors students mentored as department honors coordinator (3 total).
\vspace{0.2cm}
\begin{myenum}[3]
  \ifdetail {\color{NavyBlue} \fi
  \item Becca Apgar, \textit{Development and demonstration of an apparatus for assessing frost-heave susceptibility of soil} (2024).
  \item Daria Sofia Velasco-Vega, \textit{Thermal performance of thin-shell concrete dome structures} (2023). Pursuing Ph.D. at Purdue University.
  \item Emma Kratz-Bailey, \textit{Accessible methods, novel arrangement: Developing self-centering composite structural frames for highly resilient buildings} (2022).
  \ifdetail } \fi
\end{myenum}


Other mentoring activities.
\vspace{0.2cm}
\begin{myenum}[1]
  \ifdetail {\color{NavyBlue} \fi
  \item Grace Gibson, \textit{Gendered Journeys: analyzing the context, barriers, and solutions for women in public transit} (2024). Mentor for BYU Global Women's Studies Minor capstone project.
  \ifdetail } \fi
\end{myenum}



Students mentored as civil engineering capstone team mentor (26 total):
\vspace{0.2cm}
\begin{description}
  \ifdetail {\color{NavyBlue} \fi
  \item[2024--2025] Land development capacity system design. Sponsored by UDOT. Students: George Cicotte, Emily Jacobsen, Tacoma Parkinson.
  \item[2023--2024] BYU household travel survey. Sponsored by BYU Sustainability Office. Students: 
    Megan Hungerford, Ellie Johns, Kamryn Mansfield, and Myrranda Salmon.
  \item[2022--2023] SR-140 Corridor alternatives. Sponsored by Bluffdale City. Students:
    Clinton Childers, Robert Mickelson, Trevor Mickelson, and Joseph Wells.
  \item[2021--2022] BYU household travel survey. Sponsored by BYU Sustainability Office. Students: Nicole Adams, Hayden Atchley, Kyle Leatham, and Daniel Jarvis.
  \item[2020--2021] Forecasting demand for future FrontRunner scenarios. Sponsored by Utah Transit Authority. Students: Gillian Martin Riches, Tomas Barriga, Landon Pratt, and Cole Larsen.
  \ifdetail } \fi
  \item[2019--2020] UTA microtransit pilot evaluation. Sponsored by Utah Transit Authority. Students: Christian Hunter, Austin Martinez, and Elizabeth Smith.
  \item[2018--2019] Demand for wheelchair-accessible vehicles. Sponsored by Utah Transit Authority. Students: Nate Lant, Byron Yates, Cody Irons, and Matthew Strong.
\end{description}


% \section{Professional \\Experience}
% {\acc Singapore Mission of the Church of Jesus Christ of Latter-day Saints}
%
% \vspace{-.3cm}
% \textit{ Missionary} \hfill {June 2004 - June 2006}\\
% Served as volunteer cleric in Singapore, Malaysia, and Sri Lanka.



%% ============================================================================
\section{Awards and\\ Honors}
\begin{description}
  \ifdetail {\color{NavyBlue} \fi
\item[\acc{Most Influential Faculty}] Given to the faculty member in the Civil Engineering program
whom graduating seniors name as the most influential on their undergraduate
education. Awarded by 2022 graduating class.
\item{\acc{TUM Global Visiting Professor}} Selected to enrich the vibrant research culture at 
the Technische Universit\"at M\"unchen by virtue of innovative approaches and to explore new, cutting-edge research fields. Awarded in 2023.
\item[\acc{ASCE ExCEEd Teaching Fellow}] Participated in week-long intensive teacher
development program. Class of 2022.
\ifdetail} \fi
\item[\acc{Dwight David Eisenhower Graduate Fellowship}] Full doctoral funding from
the Federal Highways Administration 2011-2013, one of five awards nationally.
Awarded supplemental grant in 2013.
\item[\acc Eno Center for Transportation Leadership Development Conference]
Participated in the 2012 program; nominated by the Ivan Allen, Jr.\ College of
Liberal Arts at Georgia Tech.
%\item[\acc Parsons Brinckerhoff - Jim Lammie Engineering Scholarship] Awarded
%to the top engineer in the 2011 American Public Transportation Foundation (APTF)
%competition. Sponsored by Mike Allegra, general manager of the Utah Transit
%Authority. Renewed in 2012.
%% Lesser awards (comment out for space saving)
%\item[\acc Gordon W. Schultz Graduate Fellowship] Given to the Georgia Tech
%student in travel demand modeling who exhibits innovation, problem-solving, and
%practical application.
%\item[\acc National Science Foundation Graduate Fellowship Program] Honorable
%Mention in 2011 and 2012, as a first- and second-year graduate student.
%\item[\acc Jim McGee Memorial Scholarship] Cash award from the Georgia chapter of the
%American Society of Highway Engineers, one of two awards in 2011.
%\item[\acc Georgia Department of Transportation Scholarship] One of ten cash awards in
%2010 to students from the southeastern United States.
%\item[\acc Office of Research and Creative Activities (ORCA) Grant] Competitive
%research grant to survey Chinese transportation planning practices, one of
%several undergraduate research awards from Brigham Young University.
%\item[\acc Freeman-Asia Award] Grant to study Chinese finance and globalized
%engineering at Nanjing University in the People's Republic of China from the
%Institute for International Education.
\end{description}

%% ============================================================================
\section{External \\ Citizenship}



Peer review panel member, NCHRP 08-184, \textit{Framework for Assessing Induced Demand Effects of Various Roadway Investments}. (2023 --- )


Transportation Research Board of the National Academies of Science:

\begin{itemize}
  \item AEP50: Travel Demand Forecasting Member of the committee (2019 --- 2025) on
  travel demand forecasting. Chair of the travel forecasting resources
  subcommittee and editor of \url{tfresource.org}.
  \item AMS20: Economics and Land Development Member of the committee (2014
  --- 2022). 
  \item Young Members Council (2019 --- 2021). Planning and Environment subcommittee
  chair.
\end{itemize}


Reviewer for the following journals:

\begin{itemize}
  \item Transportation Research Part A: Policy and Practice
  \item Smart Cities
  \item Transportation Research Record
  \item Environment and Planning B: Urban Analytics and City Science
  \item International Journal of Sustainable Transport
  \item Journal of Public Transportation
\end{itemize}

Member, Provo City Transportation and Mobility Advisory Commission (2022 --- ). Appointed by Mayor Michelle Kaufusi.

Member of the following professional organizations:

\begin{itemize}
  \item American Society of Civil Engineers (2022 --- )
  \item Zephyr Foundation (2020 --- 2022).
  \item Institute of Transportation Engineers (2009---2013, 2018---2020)
  \item Tau Beta Pi (Utah $\beta$ '09).
  \item Young Professionals in Transportation (2013-2018); organizing co-chair of
Triangle NC chapter.
  \item American Public Transportation Association scholar task force (2011 - 2013).
\end{itemize}


\section{Media}
Anderson, T.W. (2025). Shadow lobbying, an AI paper and a willing Senator. The story behind the bill that took SLC’s streets away. \textit{Building Salt Lake}. Quoted expert opinion. July 7, 2025. \url{https://buildingsaltlake.com/shadow-lobbying-an-ai-paper-and-a-willing-senator-the-story-behind-the-bill-that-took-slcs-streets-away/}

DeBrule, D. (2024). E-scooter safety top of mind after mother's death. \textit{Fox 13 Salt Lake City}. Quoted expert opinion. March 27th, 2024. \url{https://www.fox13now.com/news/local-news/e-scooter-safety-top-of-mind-after-mothers-death}

Carlisle, N. (2022). Here’s what it might cost to ride the Little Cottonwood Canyon gondola. \textit{Fox 13 Salt Lake City}. Quoted expert opinion. November 16th, 2022. \url{https://www.fox13now.com/news/fox-13-investigates/heres-what-it-might-cost-to-ride-the-little-cottonwood-canyon-gondola}.

McCann, A. (2021). Best and worst cities to drive in. \textit{WalletHub}. Quoted expert opinion. August 31, 2021. \url{https://wallethub.com/edu/best-worst-cities-to-drive-in/13964#expert=Gregory_Macfarlane}

\textbf{Macfarlane, G.S.}. (2020). No, Utah County does not have to choose between preservation and growth. \textit{Deseret News}. Guest Opinion, August 21, 2020. \url{https://www.deseret.com/opinion/2020/8/21/21376479/}

\section{Internal \\ Citizenship}
\begin{description}
  \item[Department undergraduate committee] Co-Chair (2023 --- ), Member (2021 --- ). Lead curriculum revisions for civil engineering program and ABET accreditation / continuous improvement efforts.
  \item[Office of Civic Engagement] Faculty advisory committee member (2023 --- ). Participate in decisions related to the civic engagement minor and advise on campus activities.
  \item[Department honors coordinator] (2019 --- ). Encourage students to
  participate in the honors program, and participate on honors thesis committees
  in the department.
  \item[Department faculty development and capital improvement committee] (2018 --- 2021).
\end{description}


%% ==========================================

% \noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
% \section{Skills}
% Significant computer software and programming ability, including expert skills
% in R, \LaTeX, and git. Also experienced with Java, C, Python, QGIS,
% Cube/Voyager,  Matlab, PTV Vissim / Visum, TransCAD (with GISDK).


%\clearpage
%\thispagestyle{empty}
%\section{References}
%\textit{ Rick Donnelly, Ph.D., AICP} \\
%6100 Uptown Boulevard NE, Suite 700, Albuquerque, NM 87110 \\
%DonnellyR@pbworld.com 1.505.878.6524
%
%\textit{ Leta F. Huntsinger, Ph.D., PE} \\
%434 Fayetteville Drive, Suite 1500, Raleigh NC 27601 \\
%Huntsinger@pbworld.com 1.919.836.4086
%
%%\textit{ Laurie A. Garrow, Ph.D.} \\
%%790 Atlantic Drive, Atlanta GA 30332-0355\\
%%laurie.garrow@ce.gatech.edu 1.404.385.6634
%
%\textit{ Juan Moreno-Cruz, Ph.D.} \\
%221 Bobby Dodd Way, Atlanta GA 30332\\
%juan.moreno-cruz@econ.gatech.edu 1.404.385.1100
%
%\textit{ Kari E. Watkins, Ph.D., P.E.} \\
%790 Atlantic Drive, Atlanta GA 30332-0355\\
%kari.watkins@ce.gatech.edu 1.206.250.4415
%
%%\textit{ Patricia L. Mokhtarian, Ph.D.} \\
%%790 Atlantic Drive, Atlanta GA 30332-0355\\
%%patmokh@ce.gatech.edu 1.404.385.1443
%
%%\textit{ Patrick S. McCarthy, Ph.D.} \\
%%221 Bobby Dodd Way, Atlanta GA 30332\\
%%mccarthy@gatech.edu 1.404.894.4914
%
%%\textit{ Mitsuru Saito, Ph.D., P.E.} \\
%368J Clyde Building, Provo UT 84602\\
%msaito@byu.edu 1.801.422.6326
\end{resume}
%\vfill\moveleft.25\hoffset\centerline{References are available upon request.}



\end{document}
